The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-11-24 VonHolzenBergmann_MPMetaAnalysis.tex
Monster Paper update
incorporated Christina's comments from the summer, finished Discussion, updated references

  \title{The development of infants' responses to mispronunciations: A
Meta-Analysis}
    \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
Bergmann\textsuperscript{3,4}}
    \date{}

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon; infancy}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to Katie Von
Holzen, 0221A LeFrak Hall, University of Maryland, College Park, MD
20742. E-mail:
\href{mailto:katie.m.vonholzen@gmail.com}{\nolinkurl{katie.m.vonholzen@gmail.com}}}

\abstract{
As they develop into mature speakers of their native language, infants
must not only learn words but also the sounds that make up those words.
To do so, they must strike a balance between accepting some variation
(e.g.~mood, voice, accent), but appropriately rejecting variation when
it changes a word's meaning (e.g.~cat vs.~hat). We focus on studies
investigating infants' ability to detect mispronunciations in familiar
words, which we refer to as mispronunciation sensitivity. The goal of
this meta-analysis was to evaluate the development of mispronunciation
sensitivity in infancy, allowing for a test of competing mainstream
theoretical frameworks. The results show that although infants are
sensitive to mispronunciations, they still accept these altered forms as
labels for target objects. Interestingly, this ability is not modulated
by age or vocabulary size, challenging existing theories and suggesting
that a mature understanding of native language phonology is present in
infants from an early age, possibly before the vocabulary explosion.
Despite this finding, we discuss potential data analysis choices that
may influence different conclusions about mispronunciation sensitivity
development as well as offer recommendations to improve best practices
in the study of mispronunciation sensitivity.

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\section{Introduction}\label{introduction}

At the turn of the millenium, infant language acquisition researchers
had established that during their first two years of life, infants are
sensitive to changes in the phonetic detail of newly segmented words
(Jusczyk \& Aslin, 1995) and learned minimal pairs (Stager \& Werker,
1997). Furthermore, when presented with familiar image pairs, children
fixate on the referent of a spoken label (Fernald, Pinto, Swingley,
Weinberg, \& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and
Aslin (2000) were the first to tie these lines of research together and
investigate mispronunciation sensitivity in infant familiar word
recognition: Children aged 18 to 23 months learning American English saw
pairs of images (e.g.~a baby and a dog) and their eye movements to each
image were recorded. On \enquote{correct} trials, children heard the
correct label for one of the images (e.g. \enquote{baby}). On
\enquote{mispronounced} trials, children heard a mispronounced label of
one of the images (e.g. \enquote{vaby}). The mean proportion of
fixations to the target image (here: a baby) was calculated separately
for both correct and mispronounced trials by dividing the target looking
time by the sum of total looking time to both target and a distractor
(proportion of target looking or PTL). Mean fixations in correct trials
were significantly greater than in mispronounced trials, and in both
conditions looks to the target were significantly greater than chance.
We refer to this pattern of a difference between looks to correct and
mispronounced words as \emph{mispronunciation sensitivity} and of looks
to the target image above chance in each condition as \emph{object
identification}. Swingley and Aslin (2000) concluded that already before
the second birthday, children represent words with sufficient detail to
be sensitive to mispronunciations.

In a mature phono-lexical system, word recognition must balance
flexibility to slight variation (e.g., speaker identity, accented
speech) while distinguishing between phonological contrasts that
differentiate words in a given language (e.g.~cat-hat). The study of
Swingley and Aslin (2000) as well as subsequent studies examining
mispronunciation sensitivity probe this latter distinction. Phonological
contrasts relevant for the infant language-learner are determined by
their native language. For an infant learning Catalan, the vowel
contrast /e/-/E/ signifies a change in meaning, whereas this is not the
case for an infant learning Spanish. These contrasts are therefore not
inate, but must be learned. In this meta-analysis, we focus on infants'
developing ability to correctly apply the phonological distinctions for
their native language during word recognition. By aggregating all
publicly available evidence using meta-analysis, we can examine
developmental trends making use of data from a much larger and diverse
sample of infants than is possible in most single studies (see Frank et
al. (2017); for a notable exception). Before we outline the
meta-analytical approach and its advantages in detail, we first discuss
the proposals this study seeks to disentangle and the data supporting
each of the accounts.

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 8 to 10
months (Bergelson \& Swingley, 2017), indicating that from early stages
of the developing lexicon onwards, infants can and do detect
mispronunciations. Regarding the change in mispronunciation sensitivity
over development, however, only about half of studies have compared more
than one age group on the same mispronunciation task (see Table 1).
Across single studies all possible patterns of development lined out
above have been reported, making the current meta-analysis very
informative.

Several studies have found evidence for \emph{greater} mispronunciation
sensitivity as children develop. More precisely, the difference in
target looking for correct and mispronounced trials is reported to be
smaller in younger infants and grows as infants develop. Mani and
Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
English; although all three groups were sensitive to mispronunciations,
15-month-olds showed a less robust sensitivity. An increase in
sensitivity to mispronunciations has also been found from 20 to 24
months (Feest \& Fikkert, 2015) and 15 to 18 months (Altvater-Mackensen,
Feest, \& Fikkert, 2014) in Dutch infants, as well as German infants
from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, Feest and
Fikkert (2015) found that sensitivity to specific kinds of
mispronunciations develop at different ages depending on language
infants are learning. In other words, the native language constraints
which \emph{kinds} of mispronunciations infants are sensitive to first,
and that as infants develop, they become sensitive to other
mispronunciations.

@@

Why would mispronunciation sensitivity change as infants develop?
Typically, a change in mispronunciation sensitivity is thought to occur
along with an increase in vocabulary size, particularly with the
vocabulary spurt at about 18 months. As infants learn more words, their
focus shifts to the relevant phonetic dimensions needed for word
recognition. For example, an infant who knows a handful of words with
few phonological neighbors would not need to have fully specified
phonological representations in order to differentiate between these
words. As more phonologically similar words are learned, however, the
need for fully detailed phonological representations increases
(Charles-Luce \& Luce, 1995). Furthermore, a growing vocabulary also
reflects increased experience or familiarity with words, which may
sharpen the detail of their phonological representation (Barton, Miller,
\& Macken, 1980). If vocabulary growth leads to an increase in the
phonological specificity of infants' word representation, we should find
a relationship between vocabulary size and mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Bailey \& Plunkett, 2002; Ballem \& Plunkett,
2005; Mani \& Plunkett, 2007; Mani, Coleman, \& Plunkett, 2008;
Swingley, 2009; Swingley \& Aslin, 2000, 2002; Zesiger et al., 2012).
One notable exception comes from Mani and Plunkett (2010). Here,
12-month-old infants were divided into a low and high vocabulary group
based on median vocabulary size. High vocabulary infants showed greater
sensitivity to vowel mispronunciations than low vocabulary infants,
although this was not the case for consonant mispronunciations. Taken
together, there is very little evidence for a role of vocabulary size in
mispronunciation sensitivity. In our current meta-analysis, we include
the relationship between mispronunciation sensitivity and vocabulary
size to better understand the variation in experimental results.

Although all mispronunciation sensitivity studies are generally
interested in the the phonological detail with which infants represent
familiar words, many studies pose more nuanced questions. These
questions concern issues at the intersection of phonological development
and lexical processing and often result in manipulations of the stimuli
and experimental procedure. These manipulations may impact our overall
estimate of the effect size of mispronunciation sensitivity. Next to the
core investigation of the shape of development of infants'
mispronunciation sensitivity, we take the opportunity of a systematic
aggregation of data to address these questions and the influence of
these manipulations on infants' ability to detect mispronunciations and
how this may change with development.

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (Bernier \& White, 2017; Tamasi, 2016; White \&
Morgan, 2008) and vowel (Mani \& Plunkett, 2011) feature changes. The
greater the number of features changed, or \emph{mispronunciation size},
the easier it may be to detect a mispronunciation, whereas more similar
mispronunciations may be more difficult to detect.

Although most research examining sensitivity to mispronunciations
follows a similar design, there are some notable differences. For
example, Swingley and Aslin (2000) presented infants with pairs of
familiar images, one serving as the labeled target and one as the
unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
infants with pairs of familiar (labeled target) and unfamiliar
(unlabeled distractor) objects. By using an unfamiliar object as a
distractor, the infant is presented with a viable option onto which the
mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
Hansen, 2003). Infants ages 24 and 30 months associate a novel label
with an unfamiliar object, although only 30-month-olds retained this
label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
18-month-olds did not learn to associate a novel label with an
unfamiliar object, providing evidence that this ability is developing
from 18 to 30 months. We may find that if mispronunciation sensitivity
changes as children develop, that this change is modulated by
\emph{distractor familiarity}: whether the distractor used is familiar
or unfamiliar. Although mispronunciation sensitivity in the presence of
a familiar compared to unfamiliar distractor has not been directly
compared, the baseline preference for familiar compared to novel stimuli
is also thought to change as infants develop (Hunter \& Ames, 1988).
Furthermore, young children have been found to look longer at objects
for which they know the name, compared to objects of an unknown name
(Schafer \& Plukett, 1998). In other words, in absentia of a label,
infants may be more or less likely to fixate on an unfamiliar object. To
account for inherent preferences to the target or distractor image,
mispronunciation experiments typically compare the increase in fixations
to the target image from a silent baseline to post-labeling or present
the same yoked pairs of target and distractor images in in both a
correct and mispronounced labelling context. Considering this evidence,
we may expect that in older, but not younger, children, the presence of
an unfamiliar distractor may lead to greater mispronunciation
sensitivity than in the presence of a familiar distractor.

Furthermore, when presenting infants with a familiar distractor image,
some studies control the \emph{phonological overlap between target and
distractor labels}. For example, when examining sensitivity to a
mispronunciation of the target word \enquote{dog}, the vowel
mispronunciation \enquote{dag} would be paired with a distractor image
that shares onset overlap, such as \enquote{duck}. This ensures that
infants can not use the onset of the word to differentiate between the
target and distractor images (Fernald, Swingley, \& Pinto, 2001).
Instead, infants must pay attention to the mispronounced phoneme in
order to successfully detect the change. The influence of distractor
overlap also depends on the \emph{position of mispronunciation} in the
word, which can be at word onset, medial, or final positions. Models of
spoken word processing place more or less importance on the position of
a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
1989) describes lexical access in one direction, with the importance of
each phoneme decreasing as its position comes later in the word. In
contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
access as constantly updating and reevaluating the incoming speech input
in the search for the correct lexical entry, and therefore can recover
from word onset and to a lesser extent medial mispronunciations.

TRACE has also been used to model infants' sensitivity to
mispronunciation position (Mayor \& Plunkett, 2014), finding that as
lexicon size increases, so does sensitivity to onset mispronunciations,
whereas medial mispronunciations do not experience similar growth. In
early language acquisition, infants typically know more consonant
compared to vowel onset words. When tested on their recognition of
familiar words, therefore, younger infants would show greater
sensitivity to onset mispronunciations, which are frequently consonant
mispronunciations. The prevalence of consonant onset words may
contribute to the finding that consonants carry more weight in lexical
processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
recent review). In mispronunciation sensitivity, this would translate to
consonant mispronunciations impairing word recognition to a greater
degree than vowel mispronunciations. Yet, the handful of studies
directly comparing sensitivity to consonant and vowel mispronunciations
mostly find symmetry as opposed to an asymmetry between consonants and
vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
and vowel mispronunciations. One study did find weak evidence for
greater sensitivity to consonant compared to vowel mispronunciations
(Swingley, 2016). The English-learning infants tested by Swingley were
older than previous studies (mean age 28 months). In word learning, the
C-bias has been found to develop later in English learning infants
(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
synthesize studies examining sensitivity to the \emph{type of
mispronunciation}, whether consonant or vowel, across different ages to
determine whether infants generally exhibit more sensitivity to
consonant compared to vowel mispronunciations in familiar word
recognition as predicted by a learned account of C-bias emergence
(Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016). We
further examine the impact of language family on mispronunciation
sensitivity to consonants and vowels, as C-bias emergence has been found
to have a different developmental trajectory for Romance (French,
Italian) compared to Germanic (British English, Danish) languages (Nazzi
et al., 2016).

Finally, mispronunciation sensitivity in infants has been examined in
many different languages, such as English, Spanish, French, Dutch,
German, Catalan, Danish, and Mandarin Chinese (see Table 1). Infants
learning different languages have different ages of acquisition for
words in their early lexicon, leaving direct comparisons between
languages within the same study difficult and as a result rare. Although
we do not explicitly compare overall mispronunciation sensitivity by
language (although see previous paragraph for rationale to test by
language family), we assess evidence of mispronunciation sensitivity
from many different languages using a meta-analytic approach.

In sum, the studies we have reviewed begin to paint a picture of the
development of infants' mispronunciation sensitivity. Each study
contributes one separate brushstroke and it is only by examining all of
them together that we can achieve a better understanding of the big
picture of early language development. Meta-analyses can provide unique
insights by estimating the population effect, both of infants' responses
to correct and mispronounced labels, and of their mispronunciations
sensitivity. Because we aggregate data over various age groups, this
meta-analysis can also investigate the role of maturation by assessing
the impact of age and vocabulary size. We also make hands-on
recommendations for experiment planning, for example by providing an
effect size estimate for a priori power analyses (Bergmann et al.,
2018).

\section{Methods}\label{methods}

@@

\subsection{(Insert Figure 1 about
here)}\label{insert-figure-1-about-here}

@@

\subsection{Study Selection}\label{study-selection}

@@

\subsection{(Insert Table 1 about
here)}\label{insert-table-1-about-here}

\subsection{Data Entry}\label{data-entry}

@@

1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;\\
4 Size of mispronunciation, measured in features changed;\\
5 Distractor familiarity: familiar or unfamiliar;\\
6 Phonological overlap between target and distractor: onset,
onset/medial, rhyme, none, novel word;\\
7 Position of mispronunciation: onset, medial, offset, or mixed;\\
8 Type of mispronunciation: consonant, vowel, or both.

A detailed explanation for moderating factors 3-8 can be found in their
respective sections in the Results.\footnote{Two papers tested bilingual
  infants (Ramon-Casas \& Bosch, 2010; Ramon-Casas et al., 2011),
  yielding 2 and 4 experimental conditions. Due to this small number, we
  do not investigate the role of multilingualism, but do note that
  removing these papers from the meta-analysis did not alter the pattern
  of results.} We separated conditions according to whether or not the
target word was mispronounced to be able to investigate infants' looking
to the target picture as well as their mispronunciation sensitivity,
which is the difference between looks to the target in correct and
mispronounced trials. When the same infants were further exposed to
multiple mispronunciation conditions and the results were reported
separately in the paper, we also entered each condition as a separate
row (e.g., consonant versus vowel mispronunciations; Mani \& Plunkett,
2007). The fact that the same infants contributed data to multiple rows
(minimally those containing information on correct and mispronounced
trials) leads to shared variance across effect sizes, which we account
for in our analyses (see next section). We will call each row a record;
in total there were 251 records in our data.

\subsection{Data analysis}\label{data-analysis}

@@

\subsection{Publication Bias}\label{publication-bias}

>>>>

  \title{The development of infants' responses to mispronunciations: A Meta-Analysis}
    \author{Katie Von Holzen\textsuperscript{1,2,3}~\& Christina Bergmann\textsuperscript{4,5}}
    \date{}

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund\\\textsuperscript{2} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{3} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{4} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{5} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon; infancy}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to Katie Von Holzen, Emil-Figge-Straße 50, 44221 Dortmund, Germany. E-mail: \href{mailto:katie.m.vonholzen@gmail.com}{\nolinkurl{katie.m.vonholzen@gmail.com}}}

\abstract{
As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting the speaker's variation (e.g.~mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g.~cat vs.~hat). We focus on studies investigating infants' ability to detect mispronunciations in familiar words, which we refer to as mispronunciation sensitivity. The goal of this meta-analysis was to evaluate the development of mispronunciation sensitivity in infancy, allowing for a test of competing mainstream theoretical frameworks. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion.Further examining our findings, we shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

At the turn of the millenium, infant language acquisition researchers had established that during their first two years of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk \& Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997). Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label (Fernald, Pinto, Swingley, Weinberg, \& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate how infants interpret phonological variation in familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g.~a baby and a dog) and their eye movements to each image were recorded. On \enquote{correct} trials, children heard the correct label for one of the images (e.g.~\enquote{baby}). On \enquote{mispronounced} trials, children heard a mispronounced label of one of the images (e.g.~\enquote{vaby}). Although infants looked at the correct, target image in response to both types of trials, correct trials elicited a greater proportion of looks to the correct, target image than mispronounced trials. Swingley and Aslin (2000) concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts that differentiate words in a given language (e.g.~cat-hat). The study of Swingley and Aslin (2000) as well as subsequent studies examining infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm probe this latter distinction. Phonological contrasts relevant for the infant language-learner are determined by their native language. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. These contrasts are therefore not innate, but must be learned. In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see Frank, Braginsky, Yurovsky, and Marchman (2017); ManyBabiesConsortium (n.d.); for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

Research following the seminal study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 8 to 10 months (Bergelson \& Swingley, 2017), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1). Those studies find all possible patterns of development (see below), rendering conclusions regarding developmental change in mispronunciation sensitivity difficult.

Several studies have found evidence for \emph{greater} mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (Feest \& Fikkert, 2015) and 15 to 18 months (Altvater-Mackensen, Feest, \& Fikkert, 2014) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010).

@@

Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences. As infants develop, the rate at which they learn words increases and their focus shifts to the relevant phonetic dimensions needed for word recognition. For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words. As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases (Charles-Luce \& Luce, 1995). Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation (Barton, Miller, \& Macken, 1980). If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship (Bailey \& Plunkett, 2002; Ballem \& Plunkett, 2005; Mani, Coleman, \& Plunkett, 2008; Mani \& Plunkett, 2007; Swingley, 2009; Swingley \& Aslin, 2000, 2002; Zesiger et al., 2012). One notable exception comes from Mani and Plunkett (2010). Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand the variation in experimental results.

An alternative explanation is the level of task difficulty infants are presented with in mispronunciation sensitivity experiments. Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework {[}Processing Rich Information from Multidimensional Interactive Representations; Curtin, Byers-Heinlein, and Werker (2011); Curtin and Werker (2007); Werker and Curtin (2005)) describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands (discrimination vs.~word learning) probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset phoneme, infants' ability to access the phonological detail of familiar words may be restricted.

These manipulations may impact task demands, but they are also theoretically interesting, focus on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploatory analyses. We outline below first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants' sensitivity to factors that change the identity of a word on a measurable level (i.e.~1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant (Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011) feature changes. This also has consequences for task demands, as the greater the number of features changed, or \emph{mispronunciation size}, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.

Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. The \emph{position of mispronunciation} in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations resulting in a more demanding task than medial or coda mispronunciations.

In order to study the influence of mispronunciation position, many studies control the \emph{phonological overlap between target and distractor labels}. For example, when examining sensitivity to a mispronunciation of the target word \enquote{dog}, the vowel mispronunciation \enquote{dag} would be paired with a distractor image that shares onset overlap, such as \enquote{duck}. This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, \& Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

Consonantal changes may be more disruptive to lexical processing than vowel changes (Nazzi \& Cutler, 2018), which has been extended to infancy (Nazzi, Poltrock, \& Von Holzen, 2016). In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \& Plunkett, 2007, 2010) and Danish-learning 20-month-olds (Højen et al., n.d.) demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016). The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English- than French-learning infants (Floccia, Nazzi, Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia, Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the \emph{type of mispronunciation}, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel, Jenison, Kluender, \& Seidenberg, 2007; Nazzi et al., 2016). We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).

A second question is whether the non-linguistic context modulates infants' responses to mispronunciations: Most research on the topic presents infants with two known words, thus ruling out the unlabeled competitor, or distractor, as possible target. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects (Mani \& Plunkett, 2011; Skoruppa, Mani, Plunkett, Cabrol, \& Peperkamp, 2013; Swingley, 2016; White \& Morgan, 2008). By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \& Hansen, 2003). In a learning context, 24- and 30-month-olds associate a novel label with an unfamiliar object, but 18-month-olds do not, providing evidence that this ability, known as mutual exclusivity, is developing from 18 to 30 months (Bion, Borovsky, \& Fernald, 2013). We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by \emph{distractor familiarity}: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.

Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. Indeed, the majority of studies focus on infants learning English as a native language and a sufficient sample of other languages is therefore lacking. Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.

In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity. Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size. We also explore the influence of different linguistic (mispronunciation size and position, target-distractor overlap, and type of mispronunciation) and non-linguistic (distractor familiarity) demands on the study of mispronunciation sensitivity. Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses (Bergmann et al., 2018).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{insert-figure-1-about-here}{%
\subsection{(Insert Figure 1 about here)}\label{insert-figure-1-about-here}}

@@

\hypertarget{study-selection}{%
\subsection{Study Selection}\label{study-selection}}

@@

\hypertarget{insert-table-1-about-here}{%
\subsection{(Insert Table 1 about here)}\label{insert-table-1-about-here}}

\hypertarget{data-entry}{%
\subsection{Data Entry}\label{data-entry}}

@@

1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;\\
4 Size of mispronunciation, measured in features changed;\\
5 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;\\
6 Position of mispronunciation: onset, medial, offset, or mixed;\\
7 Type of mispronunciation: consonant, vowel, or both.
8 Distractor familiarity: familiar or unfamiliar;

A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results.\footnote{Two papers tested bilingual infants (Ramon-Casas \& Bosch, 2010; Ramon-Casas, Swingley, Sebastián-Gallés, \& Bosch, 2009), yielding 2 and 4 experimental conditions. Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.} We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row (e.g., consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were 251 records in our data.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

@@

\hypertarget{publication-bias}{%
\subsection{Publication Bias}\label{publication-bias}}

In the psychological sciences, there is a documented reluctance to publish null results. As a result, significant results tend to be over-reported and thus might be over-represented in our meta-analyses (see Ferguson \& Heene, 2012). To examine whether this is also the case in the mispronunciation sensitivity literature, which would bias the data analyzed in this meta-analysis, we conducted two tests. We first examined whether effect sizes are distributed as expected based on sampling error using the rank correlation test of funnel plot asymmetry with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). Effect sizes with low variance were expected to fall closer to the estimated mean, while effect sizes with high variance should show an increased, evenly-distributed spread around the estimated mean. Publication bias would lead to an uneven spread.
